Study of the hadronization of charged pions

### 2017-03-01 chap5.tex
Few corrections

Following the first round of questions from the analysis review committee, we
reflected about this implementation of error bars and possible overlap with the 
systematic errors
evaluated below. We found first that the correlation between the weights should reduce
the statistical errors. In a given bin the weights associated with each 
targets are always of similar sizes, this correlation will reduce the size of 
error bars. However, we do not see a method to properly take this 
effect fully into account in term of purely statistical error bars. In order
to solve this issue we came back to a point by the committee on the topic of 
systematic error bars (Q 24). There it was noted that some of these effects are
double counted once in the statistical error and once in the systematic. As these
errors are solely due to the acceptance correction, we decided to account them 
only in the systematic error budget. So we reverted statistical errors to equations
\ref{eq:MRError} and \ref{eq:DPtError} and keep the full systematic errors as they
were evaluated before.

@@

The large electric charge of our nuclear targets create an electric field that 
should be taken into account at our energies. Besides the fact that the nuclear 
electric field accelerates or decelerates the incoming and outgoing charged 
particles, it has some non trivial effects such as the focusing of low energy 
particles. Aste {\it et al.}~\cite{Aste:2005wc} showed that these Coulomb 
effects could be corrected for by using an effective momentum approximation at 
large momenta ({\it i.e.}, $Q^2>.5$ GeV$^2$). As our kinematics coverage is 
beyond this limit, we decided to use this approximation on the Coulomb 
correction of our data-sets. According to Aste {\it et al.}, the best effective 
potential approximation is given by $\bar V= 0.8 V_0$, where $V_0$ is the 
electrostatic potential at the center of nuclei. The latter is evaluated as 
$V_0= -3 \alpha_{EM} Z / (2 R)$, where $\alpha_{EM}$ is the fine-structure 
constant, $Z$ is the proton number, and R is the radius of nuclei. Table 
\ref{tab:Coulomb} contains the used values of $V_0$ and $\bar V$ on different 
nuclear target's analysis. The Coulomb correction is applied to both electrons 
and charged pions before calculating the plotted kinematical variables.

@@

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=10cm] {chap5-fig/HallC-Isospin.png}
\caption {}
\label{fig:RCexample}
\end{figure}

>>>>

Following the first round of questions from the analysis review committee, we
reflected about this implementation of error bars and possible overlap with the 
systematic errors evaluated below. First we found an error with how the formula
above was implemented and corrected it. This reduces the size of statistical 
error bars of the transverse momentum broadening by roughly a factor 2 to 3.

TODO See new results and re evaluate statement below.
We found first that the correlation between the weights should reduce
the statistical errors. In a given bin the weights associated with each 
targets are always of similar sizes, this correlation will reduce the size of 
error bars. However, we do not see a method to properly take this 
effect fully into account in term of purely statistical error bars. In order
to solve this issue we came back to a point by the committee on the topic of 
systematic error bars (Q 24). There it was noted that some of these effects are
double counted once in the statistical error and once in the systematic. As these
errors are solely due to the acceptance correction, we decided to account them 
only in the systematic error budget. So we reverted statistical errors to equations
\ref{eq:MRError} and \ref{eq:DPtError} and keep the full systematic errors as they
were evaluated before.

@@

The large electric charge of our nuclear targets create an electric field that 
should be taken into account at our energies. Besides the fact that the nuclear 
electric field accelerates or decelerates the incoming and outgoing charged 
particles, it has some non trivial effects such as the focusing of low energy 
particles. Aste {\it et al.}~\cite{Aste:2005wc} showed that these Coulomb 
effects could be corrected for by using an effective momentum approximation at 
large momenta ({\it i.e.}, $Q^2>.5$ GeV$^2$). As our kinematics coverage is 
beyond this limit, we decided to use this approximation on the Coulomb 
correction of our data-sets. According to Aste {\it et al.}, the best effective 
potential approximation is given by $\bar V= 0.8 V_0$, where $V_0$ is the 
electrostatic potential at the center of nuclei. The latter is evaluated as 
$V_0= -3 \alpha_{EM} Z / (2 R)$, where $\alpha_{EM}$ is the fine-structure 
constant, $Z$ is the proton number, and $R$ is the radius of the nuclei. Table 
\ref{tab:Coulomb} contains the used values of $V_0$ and $\bar V$ on different 
nuclear target's analysis. The Coulomb correction is applied to both electrons 
and charged pions before calculating the plotted kinematical variables.

@@

TODO Add figures of the effect and comment from review answers!

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=10cm] {chap5-fig/HallC-Isospin.png}
\caption {Ratios of deuteron over proton for $\pi^+$s and $\pi^-$s 
as a function of \xb at $z=0.55$ \cite{Asaturyan:2011mq}.}
\label{fig:RCexample}
\end{figure}
